Detecting Treatment-Subgroup Interactions in Clustered Data with Generalized Linear Mixed-Effects Model Trees

### 2016-09-05 pkg/glmertree/paper/treatment_interactions.Rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@964 255f4249-2263-4417-b1ea-8498779e27a7

The most important predictors of predictive accuracy were algorithm type, sample size, the number of covariates, and type of interaction (linear, piecewise or both). These effects were further assessed by means of the graphical display depicted in Figure~\ref{fig:xyplot_correlation_pw}. As Figure~\ref{fig:xyplot_correlation_pw} indicates, GLMM trees show highest predictive accuracy in datasets with purely piecewise interactions, whereas GLMMs show highest predictive accuracy in datasets with purely linear interactions. Furthermore, performance of GLMM tree is hardly affected by the number of covariates, whereas the predictive accuracy of GLMMs deteriorates when the number of covariates increases. This indicates that GLMM tree should be preferred in more exploratory situations, where the number of potential moderator variables is large, as GLMMs may do very poorly in terms of predictive accuracy, especially when interactions are piecewise. On the other hand, GLMM tree may perform poorly when in small sample sizes (i.e., $N=200$), when interactions are purely linear.

>>>>

The most important predictors of predictive accuracy were algorithm type, sample size, the number of covariates, and type of interaction (linear, piecewise or both). These effects were further assessed by means of the graphical display depicted in Figure~\ref{fig:xyplot_correlation_pw}. As Figure~\ref{fig:xyplot_correlation_pw} indicates, GLMM trees show highest predictive accuracy in datasets with purely piecewise interactions, whereas GLMMs show highest predictive accuracy in datasets with purely linear interactions. Furthermore, performance of GLMM tree is hardly affected by the number of covariates, whereas the predictive accuracy of GLMMs deteriorates when the number of covariates increases. This indicates that GLMM tree may be especially useful for exploratory purposes.
